Storm surge modelling in the Strait of Georgia

### 2014-07-22 RoughWork/manuscript.tex
Added an abstract. Still needs work

\title{Storm Surges}

\date{\today}

@@

\begin{abstract}
Abstract to be completed
\end{abstract}

>>>>

\title{Storm surge modelling in the Strait of Georgia}
\author{Nancy Soontiens, Susan Allen, Doug Latornell, Kate Le Sou\"{e}f}
\date{\today}

@@

\begin{abstract}
The Strait of Georgia is a large, semi-enclosed body of water between Vancouver Island and the mainland of British Columbia connected to the Pacific Ocean via the Strait of Juan de Fuca at the south and Johnstone Strait at the north. During the winter months, coastal communities in the Strait of Georgia are particularly susceptible to flooding caused by storm surges, a natural hazard that can occur when a strong storm coincides with high tide. Storm surge hindcasts have been produced using a three-dimensional numerical ocean model for the Strait of Georgia and the surrounding bodies of water (Strait of Juan de Fuca, Puget Sound, and Johnstone Strait) collectively known as the Salish Sea. The numerical model employs the Nucleus for European Modelling of the Ocean (NEMO) in a regional configuration. The model has been evaluated through comparisons of tidal elevation harmonics, tidal currents, and storm surge water levels with observations. Important forcing factors contributing to storm surges have been assessed, finding that the surge entering the domain from the Pacific Ocean contributes most significantly.
%needs a little more work.
\end{abstract}
